Towards Illumination Level Independence in the Dynamic Laser Speckle Analysis

### 2018-10-03 article/article_1.tex
corrigiendo la imagen en blanco y negro

\subsection{Data packages of drying ink}
\label{sec:descriptionink}
Fig. \ref{fig:system} shows the system setup of the ink sample test during drying where
a red laser was pointed to a layer of drying ink monitored by a digital camera;
the images are collected receiving two different illumination levels, because of the neutral 
density lens covering partially the laser beam \cite{REIS2016}.
The images were placed in data packages
are sampled with a time rate acquisition of $F_s=$ 12.5 hertz, being 
collected $N=400$ images by package. In total were collected $11$ packages 
(with the two different illumination levels each one) at the minutes 
$0$, $10$, $20$, $30$, $40$, $50$, $60$, $75$,$105$,$120$ and $150$ of drying process. 
\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\columnwidth]{system.eps}
\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system with the levels of illumination over a layer of drying ink.}
\label{fig:system}
\end{figure}
In each image of the packages was selected two regions, of $250\times200$ pixels, 
corresponding to the regions with two different illumination levels, 
as shown with black lines in the Fig. \ref{fig:regions}. In the right side of the \ref{fig:regions}  we have the
portion of image that was altered by the neutral density lens. The figure represents
with a color bar the result of  calculus the temporal speckle mean matrix ($\mu$) according the Eq. (\ref{eq:cont1})
showed in the Sec. \ref{subsec:deviation}. Being this value associated in the literature with
the illumination quantity in the surface of sample \cite{Nothdurft:05}; corresponding thus high values of $\mu$
to places with more illumination. 
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall_points_all.eps}
\caption{Selected regions and light intensity distribution in the ink drying test.}
\label{fig:regions}
\end{figure}
\textcolor{red}{Nesta figura 2 poderíamos colocar também as imagens cruas dos padrões de speckle}\\

>>>>

\subsection{Data packages of drying ink}
\label{sec:descriptionink}
Fig. \ref{fig:system} shows the system setup of the ink sample test during drying where
a red laser was pointed to a layer of drying ink monitored by a digital camera;
the images are collected receiving two different illumination levels, because of the neutral 
density lens covering partially the laser beam \cite{REIS2016}.
The images were placed in data packages and
are sampled with a time rate acquisition of $F_s=$ 12.5 hertz, being 
collected $N=400$ images by package. In total were collected $11$ packages 
(with the two different illumination levels each one) at the minutes 
$0$, $10$, $20$, $30$, $40$, $50$, $60$, $75$,$105$,$120$ and $150$ of drying process. 
\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\columnwidth]{system.eps}
\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system with the levels of illumination over a layer of drying ink.}
\label{fig:system}
\end{figure}
In each image of the packages were selected two regions, of $250\times200$ pixels, 
corresponding to the regions with two different illumination levels, 
as shown with red lines in the Fig. \ref{fig:regions}. In the right side of the Fig. \ref{fig:regions}  we have the
portion of image that was altered by the neutral density lens. 
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall_points_all.eps}
\caption{Selected regions and light intensity distribution in the ink drying test.}
\label{fig:regions}
\end{figure}
%\textcolor{red}{Nesta figura 2 poderíamos colocar também as imagens cruas dos padrões de speckle}\\
